---
title: "PurIST"
author:
- name: Heewon Seo
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PurIST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
Implementation of Purity Independent Subtyping of Tumors (PurIST) that was 
published in the Clinical Cancer Research (Rashid and Peng et al, 2020; 
DOI: 10.1158/1078-0432.CCR-19-1467).

## Install the package
```{r install, eval=FALSE}
intall.packages("devtools")
library(devtools)
devtools::install_github("lootpiz/PurIST")
```

## Load the package
```{r setup}
library(PurIST)
```

## A single sample classicifaction
```{r example, eval=FALSE}
prob = PurIST(dat)
```

## MetaGxPancreas subtyping
```{r metagx}
library(PurIST)
library(MetaGxPancreas)
library(data.table)

esets <- MetaGxPancreas::loadPancreasEsets()[[1]]

esetExprs <- lapply(esets, FUN=exprs)
esetNames <- names(esetExprs)
esetSamples <- lapply(esetExprs, FUN=colnames)

.tryPurIST <- function(col, names) {
    tryCatch({PurIST(structure(col, .Names=names))},
             error=function(e) {
                 return(NA)
             })
}

.PurISTExprColumns <- function(expr) apply(expr, 2, FUN=.tryPurIST, names=row.names(expr))

objList <- lapply(esetExprs, FUN=.PurISTExprColumns)

resultsDtL <- mapply(data.table, 'study'=esetNames, 'sample'=esetSamples, 'prob'=objList, SIMPLIFY=FALSE)
resultsDT <- rbindlist(resultsDtL)
resultsDT[, subtype := ifelse(prob > 0.5, "Basal-like", "Classical")]

table(resultsDT$subtype)

